HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits
reinstate heatmap, figure scale

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

Human evaluation of machine translation is a cognitively difficult task and when annotators rate or rank complete sentences we see low levels of agreement especially
for longer sentences.  
In order to extract more reliable annotations, previous research broke down evaluation into smaller components by asking humans to annotate semantic roles on the source and translation, and then to align them. 
We propose a new evaluation method which is based on semantic annotation called Universal Conceptual Cognitive Annotation(UCCA). UCCA is applicable across many languages, it provides a complete structure over sentences, and it is grounded in the words in the sentence. 
We apply UCCA only over the source or reference sentence, and not over the possibly garbled translation, 
and this makes annotation more reliable and also efficient as we can reuse labor intensive semantic annotations. We show that HUME can be reliably applied to four different target languages and that sentence level inter annotor agreement does not decrease over longer sentences.

@@

\paragraph{Annotation of Predicates}

@@

\def\iaafig #1{\includegraphics[width=7cm]{iaa_length_#1.png}}

\begin{figure*}[ht!]
\begin{tabular}{cc}

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and atomic nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure*}

\def\iaafig #1{\includegraphics[width=7cm]{iaa_heatmap_#1.png}}

%\begin{figure*}[ht!]
%\begin{tabular}{cc}
%
%
%\subfloat[English-Czech]{
%  \iaafig{cs}
%}
%&
%\subfloat[English-German]{
%  \iaafig{de}
%
%}
%\\
%
%\subfloat[English-Polish]{
%  \iaafig{pl}
%  
%}
%&
%\subfloat[English-Romanian]{
%  \iaafig{ro}
%
%}
%\end{tabular}
%\caption{Confusion matrices for each of the language pairs, plotted as heatmaps.}
%\label{fig:heatmap}
%\end{figure*}

@@

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
%\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

Human evaluation of machine translation is a cognitively difficult task and when
annotators rate or rank complete sentences, we see low levels of agreement especially
for longer sentences.  
%In order to extract more reliable annotations, previous research broke down evaluation into smaller components by asking humans to annotate semantic roles on the source and translation, and then to align them. 
In order to extract more reliable annotations, previous research broke down
evaluation into smaller components in various ways. 
We propose a new evaluation method
HUME
which is based on semantic annotation called Universal Conceptual Cognitive Annotation (UCCA). UCCA is applicable across many languages, it provides a complete structure over sentences, and it is grounded in the words in the sentence. 
We apply UCCA only over the source or reference sentence, and not over the
possibly garbled translation.
%, 
%and this makes annotation more reliable and also efficient as we can reuse labor
%intensive semantic annotations.
We show that HUME can be reliably applied to
four different target languages and that sentence level inter-annotator agreement
does not decrease over longer sentences.

@@

\paragraph{Annotation of Predicates Themselves}

@@

\def\iaafig #1{\includegraphics[width=3.8cm]{iaa_length_#1.png}}

\begin{figure}[ht!]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and atomic nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure}

@@

\def\iaafig #1{\includegraphics[width=3.8cm]{iaa_heatmap_#1.png}}

\begin{figure}[ht!]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

}
\end{tabular}
\caption{Confusion matrices for each of the language pairs, plotted as heatmaps.}
\label{fig:heatmap}
\end{figure}
